SciPy 1.0---Fundamental Algorithms for Scientific Computing in Python

### 2018-07-25 scipy-1.0/paper.tex

\pgfplotsset{compat=newest}
\usepackage{listings}

@@

\begin{lstlisting}[language=Python]
# example of a function that takes a single
# 3 dimesional typed memoryview as an argument
# this allows Cython-level handling of a NumPy
# array object
cpdef int func_new(int[:, :, :] arr):
    pass

>>>>

\pgfplotsset{compat=newest}
\usepackage{listings, textcomp}

\lstset{ %
  basicstyle=\ttfamily\footnotesize,  % size of fonts used for the code
  breaklines=true,   % automatic line breaking only at whitespace
  captionpos=b,   % sets the caption-position to bottom
  commentstyle=\color{gray},  % comment style
  keywordstyle=\color{blue},  % keyword style
  stringstyle=\color{red},  % string literal style
  upquote=true  %straight single quotes (requires textcomp)
}

@@

\begin{lstlisting}[language=Python]
# example of a function that takes a single
# 3 dimensional typed memoryview as an argument
# this allows Cython-level handling of a NumPy
# array object
cpdef int func_new(int[:, :, :] arr):
    pass
